# Create a Package

## Traditionally
- Traditionally
    * `utils::package.skeleton()`
    * manually writing `man`-files and managing `NAMESPACE`, ...
- Idea:
    - some functions and exports where defined 
    - a `README` file with instructions was created
- Problem:
    - quite inconvenient

## An improved and simpler way (1)
- Assumptions for this tutorial:
    - Rstudio is installed and also `git` is available
    - packages `devtools`, `usethis`, `roxygen2`, `testthat`, `covr` and `lintr` are installed
- Using package `usethis` to create a package skeleton (and a corresponding Rstudio project) 
    - `?usethis::create_package()`
- Note: take care to use an absolute path here if you're already in an rstudio project
- Then we can add additional parts for a good package *"selectively"*

## An improved and simpler way (2)

- These codes create a new package `urosconfpkg` and a Rstudio project
```{r, eval = FALSE}
usethis::create_package(path = "~/urosconfpkg")
```

- if Rstudio is available, it switches to the new project
- Note: one may change defaults of the `DESCRIPTION` file
```{r, eval = FALSE}
usethis::create_package(path = "~/urosconfpkg", fields = list(
  `Authors@R` = 'person(
    given = "Bernhard", family = "Meindl", 
    email = "bernhard.meindl@statistik.at", role = c("aut", "cre"))',
  License = "GPL-3",
  Version = "0.1"
))
```

## An improved and simpler way (3)
- content of the `DESCRIPTION` file (after some manual updates)
```{r comment='', echo = FALSE}
cat(strtrim(readLines("files/DESCRIPTION_1"), 60), sep = "\n")
```
