# Add functionality
## Adding R code (1)
- the `R` folder is by default empty
- we write a simple function in `R/greets.R`
- note, we're using a function from another package here!
```{r comment='', echo = FALSE}
cat(readLines("files/R/greets_nodoc.R"), sep = "\n")
```

- it is required to add the `glue` package to the `Imports` section of `DESCRIPTION`
    - easy: `usethis::use_package("glue")`
- if we use `glue::fun()`, this is all we need to do

## Adding R code (2)
- the `DESCRIPTION file now is`
```{r comment='', echo = FALSE}
cat(readLines("files/DESCRIPTION_3"), sep = "\n")
```

# Adding data
## Adding data to the package (1)
- Two possible ways:
    - 1: directly use an existing data set with `usethis::use_data()`
    - 2: use a script to generate data for improved reproducability
- We give an example for the second approach
```{r, eval = FALSE}
usethis::use_data_raw()
```

- This create a folder `data-raw` in which we can put scripts that generate data

## Adding data to the package (2)
- `data-raw/urosdata.R` is a script to generate data (note the `set.seed` call)

```{r comment='', echo = FALSE}
cat(readLines("files/data-raw/urosdata.R"), sep = "\n")
```
- we just need to source this file
- `usethis::use_data()` copies the dataset to the `data` folder and makes it available
