# Documentation

## Use roxygen (1)
- do not repeat yourself and document consistently
- make use of markdown to even further simplify the documentation
- More information [here](https://cran.r-project.org/web/packages/roxygen2/vignettes/markdown.html)

- `usethis::use_roxygen_md()` sets up everything
- **Note**: If you try to document before setting this up, you probably need to install `roxygen2md` to convert existing documentation to markdown format in advance

```{r, eval = FALSE}
remotes::install_github("r-lib/roxygen2md")
usethis::use_roxygen_md()
```

## Use roxygen (2)
- we need to document `greets()` and the dataset
- in Rstudio: `Code` $\rightarrow$ `Insert Roxygen Skeleton`
- modify `R/greets.R` (note the Markdown tags)
```{r comment='', echo = FALSE}
cat(readLines("files/R/greets.R"), sep = "\n")
```

## Use roxygen (3)
- documenting data is done via `R/data.R`
```{r comment='', echo = FALSE}
cat(readLines("files/R/data.R"), sep = "\n")
```

- update the documentation and the `NAMESPACE`

```{r, eval = FALSE}
devtools::document() # or in the Rstudio "Build"-tab
```

# Vignette
## Adding a package vignette (1)
- Package vignettes are a great way to demonstrate the functionality of your package
- Setting everything up can be done with:

```{r, eval = FALSE}
usethis::use_vignette("intro")
```

- updates `NAMESPACE` with required `Imports` and `Suggests`
- updates `DESCRIPTION` to specify the vignette builder (markdown)
- adding files that should be ignored in `git`
- creates `vignettes/intro.Rmd` with a default template

## Adding a package vignette (2)
- we modify `vignettes/intro.Rmd`

```{r comment='', echo = FALSE}
cat(readLines("files/vignettes/intro.Rmd"), sep = "\n")
```

- build with `devtools::build_vignettes()`
- will be updated whenever we build the package.
