# Use Rcpp
## Using Rcpp (1)
- Setup the package to use `Rcpp` is easy
```{r, eval = FALSE}
usethis::use_rcpp()
```

- modifies the `DESCRIPTION` file 
    * adds `Imports` and `LinkingTo` fields
- creates a `src` folder
- updates `.gitignore` and `.Rbuildignore` to exclude compiled files

## Using Rcpp (2)
- We get instructions how to update our `NAMESPACE` via roxygen2
- we update a `R/urosconfpkg-package.R` adding at the top

```{r comment='', echo = FALSE}
cat(readLines("files/R/urosconfpkg-package.R"), sep = "\n")
```

## Using Rcpp (3)
- The updated `DESCRIPTION` file now is
```{r comment='', echo = FALSE}
cat(strtrim(readLines("files/DESCRIPTION_4"), 60), sep = "\n")
```

## Using Rcpp (4)
- finishing `Rcpp` requires to add a simple C++ function
- content of `src/info.cpp`
```{r comment='', echo = FALSE}
cat(readLines("files/src/info.cpp"), sep = "\n")
```
- run `devtools::load_all()` and `devtools::document()`

## Using Rcpp (5)
- We can then either
  - write a wrapper function and export those for the cpp function
  - call it within an existing `R` function like `greets()`
```{r comment='', echo = FALSE}
cat(readLines("files/R/greets2.R"), sep = "\n")
```
