# Using CI

## Using CI (1)
- *Continous integration*: allows to automatically build, check, test and deploy our code
- runs whenever the underlying code base (typically a connected git repo) changes
- we are using *Travis CI*: ([`travis-ci.org`](https://travis-ci.org))
    - allows to build, test and check `R` packages 
    - account is required, but you can you your github.com account
    - required to authorize travis to be able to access your github repos
    - after successful authorizing and syncing the accounts, the new `urosconfpkg` repo is shown

## Using CI (2)
- telling R that we want to use travis
```{r, eval = FALSE}
usethis::use_travis()
```

- it adds a basic `.travis.yml` file
- adds this file to `.Rbuildignore`
- useful settings in `.travis.yml`
    - `warnings_are_errors: true`
    - `r_check_args: "--as-cran"`

## Using CI (3)
- additional options
```{r comment='', echo = FALSE}
cat(readLines("files/travis.yml"), sep = "\n")
```

## Using CI (4)
- further documentation: [`travis for R`](https://docs.travis-ci.com/user/languages/r)
- *additional options*:
  - `after_success:` additional steps that should be done after the package was successfully built, checked and tested can be listed
  - `deploy:`  it is possible to copy results, e.g a [`pkgdown site`](https://pkgdown.r-lib.org/)
