
# Testing the Package
## Adding Tests (1)
- Testing the package is important
- package [`testthat`](https://cran.r-project.org/package=testthat) can be used for this
- setting up the testing infrastucture is as easy as
```{r, eval = FALSE}
usethis::use_testthat()
```

- adds `testthat` to field `Suggests` in `DESCRIPTION`
- creates a folder `tests` in which the unit-tests should be placed

## Adding Tests (2)
- add as many files and tests folder `tests/testthat` as you like
- we add `files/tests/test_hello.R` (must start with `test*`)
```{r, echo = FALSE}
fs::dir_tree("files/tests")
```

- content of `tests/testthat/test_hello.R`
```{r comment='', echo = FALSE}
cat(readLines("files/tests/testthat/test_greets.R"), sep = "\n")
```

- finally, all tests can be run using `devtools::test()`

## Monitoring test coverage (1)
- *Code Coverage*: measures the percentage of code that is tested through unit tests
- we want the percentage as high as possible
- we are using package [`covr`](https://cran.r-project.org/package=covr)
- interactive: `covr::report()` returns an clickable html-widget

- provides backends to two online code coverage tools
    - [*coveralls.io*](https://coveralls.io/)
    - [*codecov.io*](https://codecov.io/)
    
## Monitoring test coverage (2)
- we are now using [*codecov.io*](https://codecov.io/)
- adding the coverage step to the package can be done with:
```{r, eval = FALSE}
usethis::use_coverage("codecov")
```

- this function
  - creates `codecov.yml` 
  - updates `.Rbuildignore`
  - updates `.travis.yml` adding
- after the package is successfully built, the code coverage is computed and uploaded

```{bash, eval = FALSE}
after_success:
  - Rscript -e 'covr::codecov()'
```

## Monitoring test coverage (3)
Link [**codecov**](https://codecov.io) and [**travis**](https://travis-ci.org)

- Login to [**codecov.io**](https://codecov.io) 
  - `Add new repository` $\rightarrow$ Select your package
  - copy `Upload Token`

- Login to [**travis-ci**](https://travis-ci.org)
    - Go to your package
    - `More options` $\rightarrow$ `Settings`
    - Under `Environment variables` add:
        * *Name*: "CODECOV_TOKEN"
        * *Value*: der Token 
